Radiance - A Web Application Environment

### 2017-03-15 els2017-radiance/paper.tex
Where the fuck did the DOS line endings come from?
Fix some major issues. Paper is now almost ready.

\documentclass{sig-alternate}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usemintedstyle[html]{borland}
\usemintedstyle[common-lisp]{pastie}
\newmintinline[code]{common-lisp}{}
\bibliographystyle{abbrv}

@@

\begin{abstract}
  %% FIXME
  Radiance\cite{radiance} is a set of libraries that provides an environment for web applications. Unlike traditional web frameworks that focus on a set of tools to support the construction and maintenance of a single application, Radiance attempts to allow one to run as many differing applications as desired in the same environment. This goal brings many advantages, as frequently there are common resources in applications that should be shared between them, but cannot, because the applications are separated and developed without regard for sharing. In order to fix this, Radiance provides an extensible interface mechanism to standardise the interaction between users of common resources. To facilitate the separation and encapsulation of the shared URL address space between applications, Radiance also provides a flexible routing mechanism.
\end{abstract}

@@

%% FIXME
Ideally, an administrator of a system will not have to touch any source code, and instead will be able to configure the system through a set of human-readable configuration files. It is, of course, still possible to configure the system through usual Lisp code, should one prefer this approach. \\

@@

>>>>

\documentclass{sig-alternate}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usemintedstyle[html]{borland}
\usemintedstyle[common-lisp]{pastie}
\newmintinline[code]{common-lisp}{}
\bibliographystyle{unsrt}

@@

\begin{abstract}
  Radiance\cite{radiance} is a set of libraries that provide an environment for web applications. By putting its focus on running multiple web services or applications within the same environment, it has developed a features that set it apart from traditional web frameworks. In particular, it shows a new approach to the way different framework features are provided, and how the routing to content is performed. These differences allow applications written against Radiance to transparently share common resources such as the HTTP server, user accounts, the authentication, and so forth with each other.
\end{abstract}

@@

An administrator of a system will not have to touch any source code, and instead can configure the system through a set of human-readable configuration files. It is, of course, still possible to configure the system through usual Lisp code as well, should one prefer this approach. \\

@@

\section{Acknowledgements}
Thanks to Joram Shrijver, Till Ehrengruber, and Fernando Borretti for feedback and suggestions on the paper.
